RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-15 doc/paper.tex
exptension...

	 \fxnote{TODO: about benchmarking in the literature...}
	 Concerning 
\subsection{Contributions of this work}

>>>>

	The progress in the SR field suffered from a lack of uniform, robust, and transparent
	benchmarking standards over the last two decade. Recently, La Cava et al.~\cite{la2021contemporary} proposed an
	open-source, reproducible benchmarking platform for SR, called SRBench. The authors extended  PMLB~\cite{olson2017pmlb},  a repository of standardized regression by 130 SR datasets for which model forms are known, see more in the aforementioned paper.\fxnote{TODO: Describe results of experimental evaluation}
\subsection{Contributions of this work}
